---
title: "Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trainingrando)
```

# 1. Generalized linear model
## 1.1 Normal distribution
### 1.1.1 Fixed effect only:
$$E[Y] = X\beta $$
Where:

* $\mathbf{X}$ is called the fixed-effect design matrix.

```{r, echo=FALSE}
print(myRandoDataFrame[,c(2,3)])
```

* $\beta= [\beta_0, \beta_{age}, \beta_{TypeofTumor}]$

### 1.1.2 Linear mixed model 

$$ \mathbf{Y} = \mathbf{X\beta} + \mathbf{Z\gamma} + \mathbf{\epsilon} $$

with 

* $\mathbf{\gamma} \sim N(0,G)$

* $\mathbf{\epsilon} \sim N(0,R)$

* $ cov[\mathbf{\gamma},\mathbf{epsilon}] = \mathbf{0}$

Note: Matrix $\mathbf{G}$ is a covariance matrix for random errors and $\mathbf{R}$ is the covariance matrix for the random errors.

$\mathbf{Y}|\mathbf{\gamma} \sim N(\mathbf{X\beta}+\mathbf{Z\gamma},\mathbf{R})$
$\mathbf{Y} \sim N(\mathbf{X\beta}+\mathbf{Z\gamma},\mathbf{V})$ with $\mathbf{V} = \mathbf{ZGZ'} + \mathbf{R}$
$\mathbf{Z}$ is called the random-effect design matrix.
$\mathbf{X}$ is called the fixed-effect design matrix.

\begin{eqnarray}
X &  & \mathrm{N}(0,1)\\
Y & \sim & \chi^2_{n-p}\\
R & \equiv & X/Y \sim t_{n-p}
\end{eqnarray}

#### with repeated measurments 
#### with random slope


## 1.2 Binomal distribution
### Logistic regressions
$$ log(\frac{p}{1-p}) = X\beta $$
# 2. Survival models
## 2.1 Cox proportional hazards model
$$ \lambda(t|X_{i}) = \lambda_0(t) * exp(\beta_1 X_{i1} + ... + \beta_p X_{ip})$$
with 

* $X_i = {X_{i1},...X_{ip}}$ be the realized values of covariates for subject i.

This expression gives the hazard fuction at time $ti$ for subject $i$ with covariate vector (explanatory variables) $Xi$.

The hazard function is 
$$ \lambda(t) = \frac{f(t)}{1-F(t)} $$
Where $f(t)$ is the time to (first) failure distribution (i.e. the failure density function).

Note: Although the failure rate, $\lambda (t)$, is often thought of as the probability that a failure occurs in a specified interval given no failure before time $t$ , it is not actually a probability because it can exceed 1. Erroneous expression of the failure rate in % could result in incorrect perception of the measure, especially if it would be measured from repairable systems and multiple systems with non-constant failure rates or different operation times. It can be defined with the aid of the reliability function, also called the survival function, $R(t)=1−F(t)$, the probability of no failure before time $t$. 
