---
title: "Training Rando"
author: "Nicolas Dubois"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This vignette aims to present how to use the training rando package.

# Design of the clinical trial
During the design of the clinical trial, the prognostic factors are listed and the number of treatment arms is defined.

## Definition of the prognotic factor(s)
Let's imagine a study with 3 prognostic factors.
For instance:

- Age group,
- Type of tumor and
- Genotype. 

```{r def, cache=FALSE}
library(trainingrando)
myprogfact <- CreatePrgFact(progfactLabel = "Age Group",progfactLevels=c("0-18 years", "19-35 years","36-60 years","> 60 years"))
myprogfact <- AddNewPrgFact(currentProgfact=myprogfact,progfactLabel = "Type of Tumor",progfactLevels=c("A", "B","C"))
myprogfact <- AddNewPrgFact(currentProgfact=myprogfact,progfactLabel = "Genotype.",progfactLevels=c("Genotype A", "Genotype B","Genotype C"))
```

## Definition of the treatment arms
Let's say that the study has four treatment arms (1:1:1:1):

- Placebo
- Treatment 1
- Treatment 2
- Treatment 3


```{r label=arm, cache=FALSE}
myArms <- ArmLevelProg(data.frame("Name" = c('Placebo', 'Treatement1','Treatement2','Treatement3')))
```

# Enter patients in the study

## Enter patients one by one

### First patient in the study
Let's say that a first patient has been recruited and is entring in the study. A treatment is then randomly assigned  to this first patient.
```{r label=first, cache=FALSE}
myRandoDataFrame <- AddFirstSubject(progfact=myprogfact,Arms=myArms)
```

### Second patient in the study
Then a second patient enters in the study. This patient has also a his prognotics factors.
```{r label=pat2, cache=FALSE}
# Generate another patient
myRandoDataFrame <- AddNextSubject(RandoDataFrame=myRandoDataFrame, progfact=myprogfact)
```

### Assign a treatment to the 2nd patient

The simplest approach is to use a randomization procedure whereby each patient has an equal probability 1/N of receiving any one of the N treatments.

```{r label=trtpat2, cache=FALSE}
myRandoDataFrame02 <- PurlyRandom(Arms=myArms,RandoDataFrame=myRandoDataFrame,usubjid="Pat-0002")
```

## Enter patients in a batch
```{r label=batch, cache=FALSE}
myRandoDataFrame <- GenStudyTrial(npat = 25, progfact = myprogfact, Arms=myArms)
```

## Response
### Create a response
The function `AddAResponse` create a response which is a constant:

$Y = \mu_0$

```{r label=resp01, cache=FALSE}
myResponse <- AddAResponse(RandoDataFrame=myRandoDataFrame,ResponseUnit='Weight (in kg)',Intercept=70)
```

### Add a fixed effect 
The function `RespAddFixedEffect` adds a fixed effect.

```{r label=repsfix, cache=FALSE}
myResponse <- RespAddFixedEffect(Response=myResponse,RandoDataFrame=myRandoDataFrame,ColID=2, BetaVector=c(-1,0,0,1))
```


### Add a residual variability
The function RespResidVar adds a residual variability which follows a normal distribution.

$Y2 = Y1 + \epsilon$

where

- $\epsilon$ follows $N(0,SD_(Replicates)$

```{r label=respresi, cache=FALSE}
myResponse <- RespResidVar(Response=myResponse,SDReplicates=10)
```

### Add residuals with a specified variance covariance matrix

```{r label=resvarcov, cache=FALSE}
myVarCovMatr <- UniformCorrelation(rho=0.5,sigma2=2,nTimePoints=6)
myepsilon <- espsilonVarCov(VarCovMatr=myVarCovMatr, nTimePoints=6, RandoDataFrame=myRandoDataFrame)
```



